### 2019-04-26 initial/notes.tex
stash

        Note that $\phi = 0, \mu \approx 0$ is conventionally CS4. The
        linearization locally has form $\pd{\delta \phi}{t} = -\delta \mu\p*{1 -
        \eta \sin I}$ and $\pd{\mu}{t} = -\eta \sin I$, so the eigenvalues are
        $\approx \mp \sqrt{\eta \sin I}$, and the two eigenvectors are $\p*{1,
        \pm \sqrt{\eta \sin I}}$.
\end{itemize}

@@

Consider when $\mu = \mu_4 - \delta \mu$

>>>>

        Note that $\phi = 0, \mu \approx 0$ is conventionally CS4. The
        linearization locally has form $\pd{\delta \phi}{t} = -\delta \mu\p*{1 -
        \eta \sin I}$ and $\pd{\delta \mu}{t} = -\eta \sin I \delta \phi$, so
        the eigenvalues are $\approx \mp \sqrt{\eta \sin I}$, and the two
        eigenvectors are $\p*{1, \pm \sqrt{\eta \sin I}}$.
\end{itemize}

@@

Note that $T$ is dominated by the time it spends near the saddle point. We
showed earlier that near CS4, $\pd{\phi}{t} \approx \delta \mu$ where $\delta
\mu = \mu - \mu_4$. Thus, we might surmise $\Delta \theta(\theta) \propto
\theta^{-1}$ for sufficiently small $\theta - \theta_4$. Far away, $T$ is
roughly constant and $\Delta \theta(\theta)$ is roughly constant.

What is ``far away''? Well, it probably depends on how affected our trajectory
is by the separatrix; far away from the saddle point, we go along contours of
roughly constant $\theta$, while close by we follow the separatrix pretty well.
We computed earlier that $\mu_{sep} \sim \sqrt{4\eta \sin I}$, so we might
expect $\mu > \mu_{sep}, \Delta \mu \sim C$, while $\mu < \mu_{sep}, \Delta
\mu \sim \delta \mu^{-1}$.

My $\mu > \mu_{sep}$ simulations don't seem to work very well, so I'll focus on
the $\delta \mu^{-1}$ case. In this case, define $\delta \mu_c: \Delta
\mu\p*{\delta \mu_c} = -\delta \mu_c$, i.e.\ the point that jumps immediately to
the saddle point. Furthermore, assume the inbound distribution is flat between
$\delta \mu_c, f^{-1}\p*{\delta \mu_c}$. TODO\@: empirically, $\mu_c \sim
\epsilon T$ is \emph{flat} with $\eta$, probably just because we're not getting
sufficiently close to the saddle point for the $\propto \sqrt{\eta}$ to kick in.

Then, we can compare the empirical Poincar\'e section of the points that cross
the separatrix versus the total predicted interval width $\delta \mu_c,
f^{-1}\p*{\delta \mu_c}$; this would predict $7.2\%, 18\%$. This does alright!

Now, one final way to think about this, and I think this is the important one:
consider if we are some $\delta \mu_0$ at $\phi = 0$ such that we barely hop the
separatrix; this corresponds to $P_{hop} = \frac{\delta \mu_0}{\mu_c}$. In order
for $\delta \mu_0$ to be hopping, $\delta \mu_\phi$ must be within $d_\phi
\approx \frac{2\pi \epsilon}{\mu}$ of the separatrix. We can compute the ratio
between $\delta \mu_0, \delta \mu_\phi$ by setting their Hamiltonian variations
equal:
\begin{align*}
    \delta H_0 &\approx -\mu_4 \delta \mu_0 + \eta \cos I \delta \mu_0
        \approx \eta^2 \cos I \sin I \delta \mu_0,\\
    \delta H_\phi &\approx -\sqrt{4\eta \sin I} \delta \mu_\phi,\\
    \frac{\delta \mu_\phi}{\delta \mu_0} &\propto
        \eta^{3/2}\cos I \sqrt{\sin I}.
\end{align*}
We can assemble
